\appendix
\section{Appendix}
\label{section:appendix}

\subsection{Traffic Attributes}
\label{section:traffic_attrs}

\begin{longtable}[c]{l | l}
    Column & Description \\
    \hline
    ID & This is a unique identifier of the accident record. \\
    Source & Indicates source of the accident report. \\
    Severity & Shows the severity of the accident, a number between 1 and 4. \\
    Start Time & Shows start time of the accident in local time zone. \\
    End Time & Shows end time of the accident in local time zone. \\
    Start Latitude & Shows latitude in GPS coordinates of the start point. \\
    Start Longitude: & Shows longitude in GPS coordinate of the start point. \\
    End Latitude & Shows latitude in GPS coordinate of the end point. \\
    End Longitude & Shows longitude in GPS coordinate of the end point. \\
    Distance(mi) & The length of the road extent affected by the accident. \\
    Description & Shows natural language description of the accident. \\
\end{longtable}

\subsection{Address Attributes}
\label{section:address_attrs}

\begin{longtable}[c]{l | l}
    Column & Description \\
    \hline
    Number & Shows the street number in address field. \\
    Street & Shows the street name in address field. \\
    City & Shows the city in address field. \\
    County & Shows the county in address field. \\
    State & Shows the state in address field. \\
    Zip Code & Shows the zipcode in address field. \\
    Country & Shows the country in address field. \\
    Timezone & Shows timezone based on the location of the accident. \\
\end{longtable}

\subsection{Weather Attributes}
\label{section:weather_attrs}

\begin{longtable}[c]{l | l}
    Column & Description \\
    \hline
    Airport Code & Denotes the closest airport-based weather station. \\
    Weather Timestamp & Shows the time-stamp of weather observation. \\
    Temperature & Shows the temperature (in Fahrenheit). \\
    Wind Chill & Shows the wind chill (in Fahrenheit). \\
    Humidity & Shows the humidity (in percentage). \\
    Pressure & Shows the air pressure (in inches). \\
    Visibility & Shows visibility (in miles). \\
    Wind Direction & Shows wind direction. \\
    Wind Speed & Shows wind speed (in miles per hour). \\
    Precipitation & Shows precipitation amount in inches, if there is any. \\
    Weather Condition & Shows the weather condition. \\
\end{longtable}

\subsection{Point-Of-Interest Attributes}
\label{section:poi_attrs}

\begin{longtable}[c]{l | l}
    Column & Description \\
    \hline
    Amenity & Indicates presence of amenity in a nearby location. \\
    Bump & Indicates presence of speed bump or hump in a nearby location. \\
    Crossing & Indicates presence of crossing in a nearby location. \\
    Give Way & Indicates presence of give way sign in a nearby location. \\
    Junction & Indicates presence of junction in a nearby location. \\
    No Exit & Indicates presence of no exit sign in a nearby location. \\
    Railway & Indicates presence of railway in a nearby location. \\
    Roundabout & Indicates presence of roundabout in a nearby location. \\
    Station & Indicates presence of station (bus, train, etc.) in a nearby location. \\
    Stop & Indicates presence of stop sign in a nearby location. \\
    Traffic Calming & Indicates presence of traffic calming means in a nearby location. \\
    Traffic Signal & Indicates presence of traffic signal in a nearby location. \\
    Turning Loop & Indicates presence of turning loop in a nearby location. \\
\end{longtable}

\subsection{Period-of-Day Attributes}
\label{section:pod_attrs}

\begin{longtable}[c]{l | l}
    Column & Description \\
    \hline
    Sunrise Sunset & Shows the period of day based on sunrise/sunset. \\
    Civil Twilight & Shows the period of day based on civil twilight. \\
    Nautical Twilight & Shows the period of day based on nautical twilight. \\
    Astronomical Twilight & Shows the period of day based on astronomical twilight. \\
\end{longtable}

\subsection{Python Code for Data Processing, Analysis, and Visualization}
\label{code:python}
\pythoncode{main.py}